Toward theories of deliberated preferences

### 2020-11-10 simple.tex
Wording

A possible objection to the usefulness of this approach should perhaps be lifted before delving into the formal descriptions of this rough sketch.
It may be argued that because this proposition needs a normative axiom, which cannot be validated empirically, it does not fare better than the alternative propositions existing in the literature. 
%\ac{SEU}, for example, also can be considered to claim to obtain reflective preferences on the basis of normative axioms.
I grant that it is impossible to get completely rid of normative axioms, because prescriptions must be linked to descriptions, and this cannot be done in a complete empirical way.
However, it is good to lighten as much as possible the content of normative axioms, and defer as much content as possible to descriptive claims. The descriptive parts of theories can be confronted to observations, a natural way to lift disagreements that has often proved useful in the history of science.
This article postulates that the normative axiom it proposes will be consensual, at least for some non trivial concrete instanciations of the proposed approach, among economists, practitioners, external observers and \acp{DM}. Furthermore, its simplicity and a priori obviousness is a strong point in its favor. It has, in some intuitive sense that cannot be described formally, less “content”, in the sense of that word used when economists argue that their theories should not have content about the preferences of the individuals (for fear of being paternalistic or dictatorial). Of course, any decision theory has content in a wider sense of imposing some structure to preferences, otherwise, the theory is void. The question is: are the restrictions imposed of a kind that can be judged acceptable with respect to the considered applications of the theory? Mandating, as is done here, that the judgments be of the sort that resists against counter-arguments seems to me to capture exactly what is desired in a prescription context.
%Arguably, the normative axiom proposed here is much weaker than those of a theory such as \ac{SEU}, in the sense of having less substance. (This claim can only be valid at an intuitive level: because \ac{SEU} does not use arguments, its axioms cannot be compared formally to mine.) 
The lack of concrete substance in its axiom does not prevent theories of \ac{DJ} to propose substantive, non-trivial claims about reflective preferences. It simply moves the debate from the world of discussions between experts about the validity of the axioms to the world of observations of acceptability of arguments by the persons to which these theories claim to be applicable.
It is also worth noting that the proposed axiom has a specific form that may permit \acp{DM} to reconstruct the reasoning proposed by the theory so as to be able to check that they apply to their situation. Detailed exploration of this aspect is deferred to future work.

>>>>

A possible objection to the usefulness of this approach should perhaps be lifted before delving into the formal descriptions of this rough sketch.
It may be argued that because this proposition needs a normative axiom, which cannot be validated empirically, it does not fare better than the alternative propositions existing in the literature. 
%\ac{SEU}, for example, also can be considered to claim to obtain reflective preferences on the basis of normative axioms.
I grant that it is impossible to get completely rid of normative axioms, because prescriptions must be linked to descriptions, and this cannot be done in a complete empirical way.
However, it is good to lighten as much as possible the content of normative axioms, and defer as much content as possible to descriptive claims. The descriptive parts of theories can be confronted to observations, a natural way to lift disagreements that has often proved useful in the history of science.
This article postulates that the normative axiom it proposes will be consensual, at least for some non trivial concrete instanciations of the proposed approach, among economists, practitioners, external observers and \acp{DM}. Furthermore, its simplicity and a priori obviousness is a strong point in its favor. It has, in some intuitive sense that cannot be described formally, less “content”, in the sense of that word used when economists argue that their theories should not have content about the preferences of the individuals (for fear of being paternalistic or dictatorial). Of course, any decision theory has content in a wider sense of imposing some structure to preferences, otherwise, the theory is void. The question is: are the restrictions imposed of a kind that can be judged acceptable with respect to the considered applications of the theory? Favoring judgments that resist against counter-arguments, as is done here, seems to me to capture exactly what is desired in a prescription context.
%Arguably, the normative axiom proposed here is much weaker than those of a theory such as \ac{SEU}, in the sense of having less substance. (This claim can only be valid at an intuitive level: because \ac{SEU} does not use arguments, its axioms cannot be compared formally to mine.) 
The lack of concrete substance in its axiom does not prevent theories of \ac{DJ} to propose substantive, non-trivial claims about reflective preferences. It simply moves the debate from the world of discussions between experts about the validity of the axioms to the world of observations of acceptability of arguments by the persons to which these theories claim to be applicable.
It is also worth noting that the proposed axiom has a specific form that may permit \acp{DM} to reconstruct the reasoning proposed by the theory so as to be able to check that they apply to their situation. Detailed exploration of this aspect is deferred to future work.
